---
title: "Programs"
author: "Lars Vilhuber"
date: "May 22, 2018"
output: 
  html_document: 
    keep_md: yes
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Program directory
This directory contains all programs necessary to run the cleaning, analysis, etc. They can be run separately, or from the master document (paper). 

## Setup
Most parameters are set in the `config.R`:
```{r setup_config}
source(file.path(rprojroot::find_rstudio_root_file(),"pathconfig.R"),echo=TRUE)
source(file.path(programs,"config.R"), echo=TRUE)
```

Any libraries needed are called and if necessary installed through `libraries.R`:

```{r setup_libraries}
source(file.path(basepath,"global-libraries.R"),echo=TRUE)
source(file.path(programs,"libraries.R"), echo=TRUE)
```



## Download the replication data from Google Sheet
The responses to the replication attempts are stored on Google Sheets. 
```{r download_replication,eval=FALSE}
source(file.path(programs,"01_download_replication.R"),echo=TRUE)
```

## Get CrossRef information
The master replication list has all the DOIs. We clean that up first, and then  look up the DOI at CrossRef.
```{r read_clean_list,cache=TRUE}
source(file.path(programs,"02_read_clean_replicationlist.R"),echo=TRUE)
```

```{r get_crossref,cache=TRUE,eval=FALSE}
source(file.path(programs,"03_get_crossref.R"),echo=TRUE)
```

```{r clean_replication,cache=TRUE}
source(file.path(programs,"04_clean_replicationlist.R"),echo=TRUE)
```





## Core analysis and figures
We can now tabulate the replications listed (not run) by journal and year:
```{r list_journals,results='asis'}
repllist4 <- readRDS(file=file.path(interwrk,"replication_list_clean.Rds"))
table1 <- repllist4 %>% group_by(journal,year) %>% filter(!is.na(journal)) %>% summarize(n=n()) %>% spread(year,n)
write.csv(table1,file.path(TexIncludes,"journal_by_year.csv"))
knitr::kable(table1)
```
We also tabulate the replication results. Note that this is a noisy measure: in some cases, when only an assessment was made, replication was set to "no", which is incorrect.

```{r list_journals2,results='asis'}

table2 <- repllist4 %>% group_by(journal,replicated_clean) %>% filter(!is.na(journal)) %>% summarize(n=n()) %>% spread(replicated_clean,n)
# the last entry is for NA
names(table2)[length(names(table2))] <- "NA"
write.csv(table2,file.path(TexIncludes,"journal_by_replicated.csv"))
knitr::kable(table2)

```
Some quality diagnostics:
```{r qa1,results='asis'}
knitr::kable(repllist4 %>% mutate(flag_issue = as.numeric(is.na(`Main Issue`))) %>% filter(!is.na(journal)) %>%  group_by(flag_issue,replicated_clean) %>% summarise(n=n())  %>% spread(flag_issue,n),caption = "Presence of notes (Main Issue)")

```

## Replicators

Overall, there were `r nrow(table(repllist4$Replicator))` Replicators.


## NOT RUN YET


The final program produces the tables and figures. 

```{r analytics,eval=FALSE}
source(file.path(programs,"05_analytics.R"),echo = TRUE)
```
