---
title: "Programs"
author: "Lars Vilhuber"
date: "May 22, 2018"
output: 
  html_document: 
    keep_md: yes
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Program directory
This directory contains all programs necessary to run the cleaning, analysis, etc. They can be run separately, or from the master document (paper). 

## Setup
Most parameters are set in the `config.R`:
```{r setup_config}
source(file.path(rprojroot::find_rstudio_root_file(),"pathconfig.R"),echo=TRUE)
source(file.path(programs,"config.R"), echo=TRUE)
```

Any libraries needed are called and if necessary installed through `libraries.R`:

```{r setup_libraries}
source(file.path(basepath,"global-libraries.R"),echo=TRUE)
source(file.path(programs,"libraries.R"), echo=TRUE)
```



## Download the replication data from Google Sheet
The responses to the replication attempts are stored on Google Sheets. 
```{r download_replication,eval=FALSE}
source(file.path(programs,"01_download_replication.R"),echo=TRUE)
```

## Read-in the local versions
The master replication list has various inconsistencies. We clean it up, and look up the DOI at CrossRef.
```{r read_replication}
source(file.path(programs,"02_clean_replicationlist.R"),echo=TRUE)
```
We can now tabulate the replications listed (not run) by journal and year:
```{r list_journals,results='asis'}
knitr::kable(repllist3 %>% group_by(journal,year) %>% filter(!is.na(journal)) %>% summarize(n=n()) %>% spread(year,n))
```








## Download the h-index data
The h-index data is manually compiled and stored on Google Sheets. This downloads those files. For instructions, see the h-index data directory. 
```{r download_h,eval=FALSE}
source(file.path(programs,"02_download_h-index.R"), echo=TRUE)
```

## Preparing and cleaning data
Both the h-index data and the replication data have some inconsistencies that need to be addressed.
```{r prep-h-index,eval=FALSE}
source(file.path(programs,"03_prep-h-index.R"), echo=TRUE)
```

```{r clean_data,eval=FALSE} 
source(file.path(programs,"04_clean_data.R"), echo=TRUE)
```

## Core analysis and figures
The final program produces the tables and figures. 

```{r analytics,eval=FALSE}
source(file.path(programs,"05_analytics.R"),echo = TRUE)
```
